A highly-available move operation for replicated trees

### 2019-05-22 paper/move-op.tex
Typeset Isabelle code in paper

\usepackage{isabelle,isabellesym}
\isabellestyle{it}
\renewenvironment{isabelle}{%
  \bigbreak\noindent\hspace{\parindent}%
  \begin{minipage}{\textwidth-\parindent}% use minipage to prevent page breaks
  \begin{isabellebody}%
  \begin{tabbing}%
}{%
  \end{tabbing}%
  \end{isabellebody}%
  \end{minipage}%
  \bigbreak%
}
\renewcommand{\isanewline}{\\}

@@

>>>>

\usepackage{lineno}
\usepackage{isabelle,isabellesym}
\isabellestyle{tt}
\renewenvironment{isabelle}{%
  \bigbreak\noindent\hspace{\parindent}%
  \begin{minipage}{\textwidth-\parindent}% use minipage to prevent page breaks
  \begin{isabellebody}%
  \begin{tabbing}%
}{%
  \end{tabbing}%
  \end{isabellebody}%
  \end{minipage}%
  \bigbreak%
}
\renewcommand{\isacartoucheopen}{}
\renewcommand{\isacartoucheclose}{}

@@

\begin{figure*}
\raggedright
\begin{isabellebody}
\internallinenumbers
\isacommand{datatype}\isamarkupfalse%
\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ operation\isanewline
\ \ {\isacharequal}\ Move\ {\isacharparenleft}move{\isacharunderscore}time{\isacharcolon}\ {\isacharprime}t{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ {\isacharparenleft}move{\isacharunderscore}parent{\isacharcolon}\ {\isacharprime}n{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ {\isacharparenleft}move{\isacharunderscore}meta{\isacharcolon}\ {\isacharprime}m{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ {\isacharparenleft}move{\isacharunderscore}child{\isacharcolon}\ {\isacharprime}n{\isacharparenright}\isanewline
\isanewline
\isacommand{datatype}\isamarkupfalse%
\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ log{\isacharunderscore}op\isanewline
\ \ {\isacharequal}\ LogMove\ {\isacharparenleft}log{\isacharunderscore}time{\isacharcolon}\ {\isacharprime}t{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}old{\isacharunderscore}parent{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m{\isacharparenright}\ option{\isacartoucheclose}{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}new{\isacharunderscore}parent{\isacharcolon}\ {\isacharprime}n{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}log{\isacharunderscore}meta{\isacharcolon}\ {\isacharprime}m{\isacharparenright}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}log{\isacharunderscore}child{\isacharcolon}\ {\isacharprime}n{\isacharparenright}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ state\ {\isacharequal}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ log{\isacharunderscore}op\ list\ {\isasymtimes}\ {\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set{\isacartoucheclose}\isanewline
\isanewline
\isacommand{definition}\isamarkupfalse%
\ get{\isacharunderscore}parent\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set\ {\isasymRightarrow}\ {\isacharprime}n\ {\isasymRightarrow}\ {\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m{\isacharparenright}\ option{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}get{\isacharunderscore}parent\ tree\ child\ {\isasymequiv}\isanewline
\ \ \ \ \ if\ {\isasymexists}{\isacharbang}parent{\isachardot}\ {\isasymexists}{\isacharbang}meta{\isachardot}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree\ then\isanewline
\ \ \ \ \ \ \ Some\ {\isacharparenleft}THE\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharparenright}{\isachardot}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree{\isacharparenright}\isanewline
\ \ \ \ \ else\ None{\isacartoucheclose}\isanewline
\isanewline
\isacommand{inductive}\isamarkupfalse%
\ ancestor\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set\ {\isasymRightarrow}\ {\isacharprime}n\ {\isasymRightarrow}\ {\isacharprime}n\ {\isasymRightarrow}\ bool{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}{\isasymlbrakk}{\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree{\isasymrbrakk}\ {\isasymLongrightarrow}\ ancestor\ tree\ parent\ child{\isacartoucheclose}\ {\isacharbar}\isanewline
\ \ {\isacartoucheopen}{\isasymlbrakk}{\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree{\isacharsemicolon}\ ancestor\ tree\ anc\ parent{\isasymrbrakk}\ {\isasymLongrightarrow}\ ancestor\ tree\ anc\ child{\isacartoucheclose}\isanewline
\isanewline
\isacommand{fun}\isamarkupfalse%
\ do{\isacharunderscore}op\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ operation\ {\isasymtimes}\ {\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set\ {\isasymRightarrow}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ log{\isacharunderscore}op\ {\isasymtimes}\ {\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}do{\isacharunderscore}op\ {\isacharparenleft}Move\ t\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}LogMove\ t\ {\isacharparenleft}get{\isacharunderscore}parent\ tree\ c{\isacharparenright}\ newp\ m\ c{\isacharcomma}\isanewline
\ \ \ \ \ \ if\ ancestor\ tree\ c\ newp\ {\isasymor}\ c\ {\isacharequal}\ newp\ then\ tree\isanewline
\ \ \ \ \ \ else\ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}\ {\isasymunion}\ {\isacharbraceleft}{\isacharparenleft}newp{\isacharcomma}\ m{\isacharcomma}\ c{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacartoucheclose}\isanewline
\isanewline
\isacommand{fun}\isamarkupfalse%
\ undo{\isacharunderscore}op\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ log{\isacharunderscore}op\ {\isasymtimes}\ {\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}undo{\isacharunderscore}op\ {\isacharparenleft}LogMove\ t\ None\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}{\isacartoucheclose}\ {\isacharbar}\isanewline
\ \ {\isacartoucheopen}undo{\isacharunderscore}op\ {\isacharparenleft}LogMove\ t\ {\isacharparenleft}Some\ {\isacharparenleft}oldp{\isacharcomma}\ oldm{\isacharparenright}{\isacharparenright}\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}\ {\isasymunion}\ {\isacharbraceleft}{\isacharparenleft}oldp{\isacharcomma}\ oldm{\isacharcomma}\ c{\isacharparenright}{\isacharbraceright}{\isacartoucheclose}\isanewline
\isanewline
\isacommand{fun}\isamarkupfalse%
\ redo{\isacharunderscore}op\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ log{\isacharunderscore}op\ {\isasymRightarrow}\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ state\ {\isasymRightarrow}\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ state{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}redo{\isacharunderscore}op\ {\isacharparenleft}LogMove\ t\ {\isacharunderscore}\ p\ m\ c{\isacharparenright}\ {\isacharparenleft}ops{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}let\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}Move\ t\ p\ m\ c{\isacharcomma}\ tree{\isacharparenright}\isanewline
\ \ \ \ \ \ in\ {\isacharparenleft}op{\isadigit{2}}\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\isanewline
\isanewline
\isacommand{fun}\isamarkupfalse%
\ interp{\isacharunderscore}op\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}t{\isacharcolon}{\isacharcolon}{\isacharbraceleft}linorder{\isacharbraceright}{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ operation\ {\isasymRightarrow}\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ state\ {\isasymRightarrow}\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ state{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}interp{\isacharunderscore}op\ op{\isadigit{1}}\ {\isacharparenleft}{\isacharbrackleft}{\isacharbrackright}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}let\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}op{\isadigit{1}}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\isanewline
\ \ \ \ \ \ in\ {\isacharparenleft}{\isacharbrackleft}op{\isadigit{2}}{\isacharbrackright}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\ {\isacharbar}\isanewline
\ \ {\isacartoucheopen}interp{\isacharunderscore}op\ op{\isadigit{1}}\ {\isacharparenleft}logop\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}if\ move{\isacharunderscore}time\ op{\isadigit{1}}\ {\isacharless}\ log{\isacharunderscore}time\ logop\isanewline
\ \ \ \ \ \ then\ redo{\isacharunderscore}op\ logop\ {\isacharparenleft}interp{\isacharunderscore}op\ op{\isadigit{1}}\ {\isacharparenleft}ops{\isacharcomma}\ undo{\isacharunderscore}op\ {\isacharparenleft}logop{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\isanewline
\ \ \ \ \ \ else\ let\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}op{\isadigit{1}}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\ in\ {\isacharparenleft}op{\isadigit{2}}\ {\isacharhash}\ logop\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\isanewline
\isanewline
\isacommand{definition}\isamarkupfalse%
\ interp{\isacharunderscore}ops\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}t{\isacharcolon}{\isacharcolon}{\isacharbraceleft}linorder{\isacharbraceright}{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ operation\ list\ {\isasymRightarrow}\ {\isacharparenleft}{\isacharprime}t{\isacharcomma}\ {\isacharprime}n{\isacharcomma}\ {\isacharprime}m{\isacharparenright}\ state{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}interp{\isacharunderscore}ops\ ops\ {\isasymequiv}\ foldl\ {\isacharparenleft}{\isasymlambda}state\ oper{\isachardot}\ interp{\isacharunderscore}op\ oper\ state{\isacharparenright}\ {\isacharparenleft}{\isacharbrackleft}{\isacharbrackright}{\isacharcomma}\ {\isacharbraceleft}{\isacharbraceright}{\isacharparenright}\ ops{\isacartoucheclose}\isanewline
\isanewline
\isacommand{definition}\isamarkupfalse%
\ unique{\isacharunderscore}parent\ {\isacharcolon}{\isacharcolon}\ {\isacartoucheopen}{\isacharparenleft}{\isacharprime}n\ {\isasymtimes}\ {\isacharprime}m\ {\isasymtimes}\ {\isacharprime}n{\isacharparenright}\ set\ {\isasymRightarrow}\ bool{\isacartoucheclose}\ \isakeyword{where}\isanewline
\ \ {\isacartoucheopen}unique{\isacharunderscore}parent\ tree\ {\isasymequiv}\ {\isacharparenleft}{\isasymforall}p{\isadigit{1}}\ p{\isadigit{2}}\ m{\isadigit{1}}\ m{\isadigit{2}}\ c{\isachardot}\ {\isacharparenleft}p{\isadigit{1}}{\isacharcomma}\ m{\isadigit{1}}{\isacharcomma}\ c{\isacharparenright}\ {\isasymin}\ tree\ {\isasymand}\ {\isacharparenleft}p{\isadigit{2}}{\isacharcomma}\ m{\isadigit{2}}{\isacharcomma}\ c{\isacharparenright}\ {\isasymin}\ tree\ {\isasymlongrightarrow}\ p{\isadigit{1}}\ {\isacharequal}\ p{\isadigit{2}}\ {\isasymand}\ m{\isadigit{1}}\ {\isacharequal}\ m{\isadigit{2}}{\isacharparenright}{\isacartoucheclose}%
\end{isabellebody}
\caption{The move operation algorithm, implemented in the Isabelle/HOL language.}
\label{fig:code}
\end{figure*}
